The Effects of Telluric Lines in Radial Velocity Searches\\ for Planets with Iodine Cells as Calibrators\altaffilmark{1}

### 2016-08-17 telluric/telluric.tex
Migrate thesis text in and adjust formats etc.

This paper characterizes and corrects for the adverse effects of
telluric contamination under the context of iodine-calibrated precise
RV, especially for the micro-telluric lines. ZZZ We first describe our
methodology for characterizing the effects of tellurics in
Section~\ref{sec:method}, then... ZZZ

%----------------------------------------------------------------
% Plot showing micro-telluric lines
% made by ~/Exo../Keck../plots_general/spec_plot.pro
\begin{figure}
\includegraphics[scale=0.5]{telluric/tellurics_all.eps} 
\caption{Telluric lines in the iodine region are mostly shallow water
lines, with some moderately deep water lines near 5900\AA\ and very
deep oxygen lines near 6300\AA. The insert plot is showing the
pervasiveness of micro-telluric lines, i.e.~$\leq$1--3\% in depths.
\label{telluric:fig:telluric}}
\end{figure}
%----------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterization of the Impacts of Micro-tellurics on RV
  Precision via Simulation}\label{keck:telluric:impact}

@@

% more on the two stars 
HD 185144 (spectral type G9V, per Simbad) has 712 \keck\ observations,
with RV RMS $=$ 2.57 m/s, and it has a relatively small barycentric
velocity (often referred to as the barycentric velocity correction, or
BC; see Chapter~\ref{chap:doppler}) span, $[-4.7,\ 4.6]$ km/s, because
it is near the north ecliptic pole. HD 10700 (spectral type G8.5V) has
623 observations, with RMS $=$ 3.05 m/s, and its BC span is $[-27.8,\
26.8]$ km/s. The RV RMS numbers quoted here come from reductions using
our version of CPS Doppler pipeline, and they are larger than the RMS
values from the most up-to-date CPS pipeline due to some recent
improvements in the CPS version. The most recent CPS inventory (as of
April 2016) also has a few new observations on these two stars.

We describe how we simulated our data and used them to characterize
the impacts of tellurics in Section~\ref{keck:telluric:method}, and
then lay out our results in Section~\ref{keck:telluric:results}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Methodology of the Simulation}\label{keck:telluric:method}

@@

% how we simulated the spectrum
Below is our recipe for simulating \keck\ spectra and DSSTs:
\begin{enumerate}
\item Generate a synthetic spectrum for the target star using
  Spectroscopy Made Easy (SME;
  \citealt{valentipiskunov1996,valentifischer2005}; the SME spectra are
  kindly provided by Jason Curtis). We refer to this spectrum as the
  input synthetic spectrum or the SME spectrum.
\item Based on the SME spectrum, generate a deconcolved stellar
  spectral template (DSST) for the target
  star. First, we redshift the SME spectrum so that it has the same
  barycentric velocity as the real DSST of the target star. Then we
  break the SME spectrum into chunks as defined by the real DSST (an IDL
  structure) of this target star.
\item Run TERRASPEC \rev{\citep{Bender2012}, a versatile software for
  synthesizing telluric spectrum (it is a wrapper around the HITRAN line
  list \citep{hitran2013} and the LBLRTM package \citep{lblrtm},
  developed by Chad Bender, who provided crucial help in this work for
  using TERRASPEC)}, to generate a telluric absorption spectrum using a
  typical Mauna Kea atmospheric condition in the summer, with
  precipitable water vapor (pwv) 1~mm (a little bit more humid than
  Keck's usual condition), and oxygen column density that is consistent
  with the altitude of the real DSST observation. We multiply this
  synthetic telluric spectrum with the SME spectrum to make a
  telluric-contaminated DSST.
\item Loop through each real observed spectrum of the target star, and
  simulate a pair of observations following this recipe:
  \begin{enumerate}
  \item Shift the SME spectrum to have the same barycentric velocity
    as the star at the epoch of the real observation (i.e., assuming
    intrinsic stellar velocity is zero).
  \item Generate a continuous wavelength solution for each echelle
      order based on the best-fit wavelength solution for the real
      spectrum. 
  \item Re-sample the SME spectrum and the iodine atlas onto a
    wavelength grid that is four times finer than the wavelength
    solution grid. Multiply the stellar spectrum with the iodine
    atlas.
  \item To add telluric contamination: multiply the simulated spectrum
    with a telluric absorption spectrum generated with TERRASPEC, again
    for typical Mauna Kea summer, with pwv $=$ 1~mm, and oxygen column
    density that is consistent with the altitude of the real observation.
  \item Determine the IP for each echelle order with two options: (1)
    a single Gaussian with $\sigma=1.7$ pixel, matching the \keck\
    resolution; (2) a sum-of-Gaussian IP derived using the average IPs for
    each echelle order. We will explain these two options later in the
    text.
  \item Convolve each order of the stellar$\times$iodine spectrum with
    the IP.
  \item Fit for the blaze function for each order of the real observed
    spectrum with a third-order polynomial using the top 1\% of the flux,
    and multiply the simulated spectrum so that they have matching ``blaze
    functions''. This also ensures that the simulated spectrum has the
    same photon counts as the real one.
  \item Add photon noise according to Poisson statistics, when
    desired.
  \end{enumerate}
\item Generate a separate data log file for each set of simulated of
  observations under the same conditions (i.e., telluric choice, IP choice,
  photon-noise choice).
\end{enumerate}

% different sets of simulations To isolate the problem of tellurics,
we first simulated spectra free of photon noise and with a simple
single Gaussian IP for the spectrograph ($\sigma = 1.7$ pixels to
match the \keck\ resolution). When extracting RVs for such sets of
simulated spectra, we fixed the IPs to the same as input and only
fitted for three free parameters. This removes the errors induced by
photon noise and uncertainties in IP fitting (which, after all,
involves 12 additional free parameters). We then added the Poisson
noise to the spectra, but still using simple and fixed IPs, to see how
the effects will change in cases with limited-SNR (as opposed to
infinite SNR). Next, we used complex IPs, the same ones as the
best-fit sum-of-Gaussian IPs found for real spectra, and float the IP
parameters when extracting RVs. \rev{For the simulated spectra with complex
IPs, we extracted their RVs following exactly the same procedure for
real observations, e.g., using IP initial guesses from solutions for
real neighboring B star $+$ iodine observations.} The conditions and
results of these three pairs of simulations are listed in
Table~\ref{telluric:tab:simulation}, and also illustrated in
Figure~\ref{telluric:fig:sim}. These results show the impacts of
telluric contamination on \keck\ data, which is discussed in the
following subsection.

%----------------------------------------------------------------
% Table: RV RMS for various simulations
\renewcommand{\arraystretch}{1.2} % more row spacing for the table
\begin{deluxetable}{ccccl}
\tabletypesize{\scriptsize}
\tablecaption{List of Simulations
\label{telluric:tab:simulation}}
\tablewidth{\textwidth}
\tablehead{
  \colhead{Simulation Conditions} & \colhead{Tellurics?} &
  \colhead{185144 RMS} &
  \colhead{10700 RMS} &
  \colhead{More Details in} 
}
\startdata
No photon noise, & No & 0.62 m/s & 1.95 m/s\tablenotemark{c} & Section~\ref{keck:telluric:results} \\ 
simple, fixed IPs & Yes & 1.21 m/s & 2.42 m/s\tablenotemark{c} & top
panels, Figure~\ref{telluric:fig:sim} \\ 
\hline
Poisson noise, & No & 2.11 m/s\tablenotemark{c} & 2.54 m/s\tablenotemark{c} & Section~\ref{keck:telluric:results} \\
simple, fixed IPs\tablenotemark{a} & Yes & 2.12 m/s\tablenotemark{c} & 2.81 m/s\tablenotemark{c} &
middle panels, Figure~\ref{telluric:fig:sim} \\ 
\hline
Poisson noise, & No & 1.22 m/s & 1.35 m/s & Section~\ref{keck:telluric:results}\\
complex, floating IPs,\tablenotemark{a} & Yes & 1.29 m/s & 1.44 m/s &
bottom panels, Figure~\ref{telluric:fig:sim} \\ 
\hline
Poisson noise, & No & 1.27 m/s & 1.43 m/s &Section~\ref{keck:telluric:masking} \\
complex, floating IPs, & Yes & 1.27 m/s & 1.43 m/s & Figure~\ref{telluric:fig:dsstmask} \\
masking the telluric pixels\tablenotemark{a} & & & & Table~\ref{telluric:tab:rmsmasking}  \\
\hline 
Poisson noise, & pwv $=$ 0.5, 0.9 & 1.28, 1.22 m/s & 1.32, 1.30 m/s &
Section~\ref{keck:telluric:neid} \\ 
complex, floating IPs, & pwv $=$ 1.0, 1.1 & 1.25, 1.23 m/s & 1.33, 1.31
m/s & Figure~\ref{telluric:fig:neid} \\ 
modeling tellurics\tablenotemark{b} 
\enddata
\tablenotetext{a}{With pairs of simulated spectra with or without
  tellurics and each pair has the same Poisson noise added.}
\tablenotetext{b}{Telluric lines added with pwv $=$ 1~mm, and we
  extracted RVs using pwv $=$ 0.5, 0.9, 1.0, 1.1~mm to access how
  accurately/precisely one needs to model the tellurics.}
\tablenotetext{c}{These simulations suffer from severe numerical and
  algorithmic errors for reasons not yet fully understood.}
\end{deluxetable}
%----------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Results of the Simulation}\label{keck:telluric:results}

%----------------------------------------------------------------
% Telluric effect, no photon noise
% plot made by ~/Exo.../Keck.../simulate.../msplot.pro
\begin{figure}
\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-rja01-rjb01.eps}}
\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-rja01-rjb01.eps}}\
\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-rjc01-rjd01.eps}}
\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-rjc01-rjd01.eps}}\
\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-test0-test1.eps}}
\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-test0-test1.eps}}\
\caption{Effects of telluric lines manifested as correlation between
  RV and BC. Each point represents the difference in RV estimates for
  a pair of simulated spectra: one without telluric absorption, and
  one with telluric absorption on top of the stellar and iodine
  spectra. {\bf Top 2 panels:} To isolate the effects of telluric
  lines, the simulated spectra used for this plot do not have Poisson
  noise added, and they have simple one-component Gaussian IPs which
  have fixed width and thus the IP parameters are all fixed to the
  true values in the RV extraction. {\bf Middle 2 panels:} same as the
  top panels, but for simulated spectra with Poisson noise (same noise
  for the telluric and non-telluric spectrum pairs; and still the same
  simple IPs). {\bf Bottom 2 panels:} same as above, but for simulated
  spectra with Poisson noise and complex IPs that are similar to the
  ones in actual observations. IP parameters are not fixed in this
  case, so the code is fitting 12 additional parameters for the IP on
  top of the 3 for wavelength solution and Doppler shift (see
  Chapter~\ref{chap:doppler} for more details on the code).
\label{telluric:fig:sim}}
\end{figure}
%----------------------------------------------------------------

% no photon noise
Figure~\ref{telluric:fig:sim} illustrates the effects of telluric
contamination under different conditions. The top panels are RV
differences between the simulated spectrum pairs with infinite SNR and
perfectly known IPs, which might somewhat represent the capability of
future precise RV instruments. These two plots highlight the net
effects of telluric contamination: they cause large biases in RV
estimates, which manifest as strong RV-BC correlations or
trends. \rev{Clearly, the current statistical weighting or ``vanking''
procedure in the Doppler code is unable to fully correct these biases.}

% adds photon noise?
Interestingly, when we added in photon noise (middle panels of
Figure~\ref{telluric:fig:sim}), the effects of telluric contamination
are washed out significantly. \rev{This is probably because photon noise
induces a much bigger RV scatter than the micro-telluric lines. This
is not surprising, given that the depths of these micro-telluric lines
are often comparable to noise level. We are still investigating the
exact reason of this ``wash out''.}

% adds complex IP 
When using complex IPs and fitting for IPs in RV extraction (bottom
panels of Figure~\ref{telluric:fig:sim}), the effects of telluric
contamination are further washed out, as we are adding in more errors
\rev{that are perhaps larger than telluric-induced ones}. We can
barely see any RV-BC correlation in the case of HD 185144 and only
some in HD 10700.

% tellurics add RV RMS
The RV-BC correlations shown in Figure~\ref{telluric:fig:sim} will
translate into spurious peaks in the periodograms of the target star,
and such spurious peaks will have periods around a sidereal year and
its harmonics. This is very damaging for the search of exoplanets in
the Habitable Zone around Sun-like stars, which would have periods
around 360 days. Besides these spurious signals, telluric
contamination also causes increases in RV RMS. In all cases of
telluric-free and telluric-contaminated simulation pairs, the RV RMS
is larger for the telluric-contaminated case
(Table~\ref{telluric:tab:simulation}). The RMS numbers written in
Figure~\ref{telluric:fig:sim} represent the amount of RV RMS added (in
quadrature) because of telluric contamination (again, the spectrum
pairs are same-noise pairs -- they only differ in terms of having or
not having telluric lines). These numbers also represent an RV RMS
floor set by the telluric contamination: for example, if we ignore
tellurics in RV reduction, one would not achieve an RV precision of
$<$0.6-0.7 m/s on G type stars using iodine cells as calibrators. This
would compromise our ability to detect Earth or super-Earth exoplanets
greatly (again, Earth 2.0 would have an RV amplitude of 0.08 m/s). In
the next section, we discuss strategies to eliminate these adverse
effects of telluric contamination for iodine-calibrated precise RV
data.

@@

%----------------------------------------------------------------
% Table: RV RMS for various simulations
\renewcommand{\arraystretch}{1.2} % more row spacing for the table
\begin{deluxetable}{ccl}
\tabletypesize{\scriptsize}
\tablecaption{Comparison of RV RMS between Simulations with or without Masking
\label{telluric:tab:rmsmasking}}
\tablewidth{320pt}
\tablehead{
  \colhead{HD 185144} & \colhead{HD 10700} & \colhead{Simulation Conditions}
}
\startdata
1.22 m/s & 1.35 m/s & No tellurics \\
1.29 m/s & 1.44 m/s & With tellurics \\
1.27 m/s & 1.43 m/s & No tellurics, but masking telluric pixels \\
1.27 m/s & 1.43 m/s & With tellurics, and masking telluric pixels
\enddata
\end{deluxetable}
%----------------------------------------------------------------

% what do I mean when I talk about masking?
The simplest solution is to mask out telluric lines in the spectrum,
which means, in practice, locate the telluric-contaminated pixels and
flag them as bad pixels in the observed spectrum so that the
least-$\chi^2$ fitter will ignore them. For \keck\ or any
iodine-calibrated RV reduction, this also means masking out the
regions corresponding to locations of telluric lines in the
deconvolved stellar reference spectrum -- because the stellar
reference spectrum was taken at a different BC, the telluric lines
therein are shifted with respect to the ones in the epoch observation
as we try to match up the stellar lines in observed and reference
spectra. This double masking procedure is illustrated in
Figure~\ref{telluric:fig:dsstmask}. This is done dynamically in
the fitting process, in the sense that, for each iteration in the
least-$\chi^2$ minimization process, the contaminated pixels are
located according to the current wavelength solution parameters in
this fitting iteration. The wavelength solution changes from iteration
to iteration, and thus the masked pixels can change too.

%----------------------------------------------------------------
% Double masking of telluric lines
% plot made by converting pdf to eps. pdf comes from slides of CfASSP
% seminar talk, which can be found in ~/Ex.../Professional../..CfASSP../.
\begin{figure}
\subfloat{\includegraphics[scale=0.5]{telluric/dsst-mask1.eps}}\\
\subfloat{\includegraphics[scale=0.5]{telluric/dsst-mask2.eps}}
\caption{Illustration for how we mask telluric contaminated
pixels. The top panel shows how we mask the telluric lines (red solid
lines) in the epoch observation taken at $t=t_e$. The bottom panel
shows why we also need to mask pixels associated with telluric lines
in the deconvolved stellar reference spectrum taken at epoch $t=t_0$
and being shifted in order to model the observation.
\label{telluric:fig:dsstmask}}
\end{figure}
%----------------------------------------------------------------

% simulations and results 
To investigate the effectiveness of masking, we performed RV
extraction on simulated spectra with or without telluric lines
injected and with or without masking (all with Poisson noise and
complex IP to mimic real observations as much as possible). For
stellar reference spectrum, we used the synthetic spectrum with
telluric lines. The results are already listed in
Table~\ref{telluric:tab:simulation}, but are listed again in
Table~\ref{telluric:tab:rmsmasking} for clear comparisons. In terms of
improving RV precision or reducing RV RMS, masking is very
ineffective. The additional errors it introduces diminish its
merits. On the other hand, masking does improve the accuracy to some
degree: for example, masking does remove the downward RV trend seen in
HD 10700 data on the bottom right plot of
Figure~\ref{telluric:fig:sim} in the BC range $[-3\times10^4,\
-2\times10^4]$ m/s. However, masking is an ineffective way to mitigate
the effects of telluric contamination overall, especially since the RV
errors and RV-BC trends are dominated by photon noise and algorithmic
errors (and other types of errors too in real observations).

@@

% how about masking in real observations?  
We also applied telluric masking in RV reduction for real
observations, and saw no improvement over RV precision or
accuracy. This is because other effects dominate rather than
tellurics, as mentioned above, such as photon and algorithmic errors
and especially deconvolution errors in stellar reference spectrum,
which are discussed in Section~\ref{keck:sec:dsst} and
\ref{keck:sec:algorithm}.

@@

\subsubsection{How precisely does one need to model the tellurics?}\label{keck:telluric:neid}

>>>>

This paper characterizes and corrects for the adverse effects of
telluric contamination under the context of iodine-calibrated precise
RV, especially for the micro-telluric lines. ZZZ We first describe our
methodology for characterizing the effects of tellurics in, then... ZZZ

%----------------------------------------------------------------
% Plot showing micro-telluric lines
% made by ~/Exo../Keck../plots_general/spec_plot.pro
\begin{figure}
\includegraphics[scale=0.3]{telluric/tellurics_all.eps} 
\caption{Telluric lines in the iodine region are mostly shallow water
lines, with some moderately deep water lines near 5900\AA\ and very
deep oxygen lines near 6300\AA. The insert plot is showing the
pervasiveness of micro-telluric lines, i.e.~$\leq$1--3\% in depths.
\label{fig:telluric}}
\end{figure}
%----------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization of the Impacts of Micro-tellurics on RV
  Precision via Simulation}\label{sec:impact}

@@

% more on the two stars 
HD 185144 (spectral type G9V, per Simbad) has 712 \keck\ observations,
with RV RMS $=$ 2.57 m/s, and it has a relatively small barycentric
velocity (often referred to as the barycentric velocity correction, or
BC) span, $[-4.7,\ 4.6]$ km/s, because
it is near the north ecliptic pole. HD 10700 (spectral type G8.5V) has
623 observations, with RMS $=$ 3.05 m/s, and its BC span is $[-27.8,\
26.8]$ km/s. The RV RMS numbers quoted here come from reductions using
our version of CPS Doppler pipeline, and they are larger than the RMS
values from the most up-to-date CPS pipeline due to some recent
improvements in the CPS version. The most recent CPS inventory (as of
April 2016) also has a few new observations on these two stars.

We describe how we simulated our data and used them to characterize
the impacts of tellurics in Section~\ref{sec:method}, and
then lay out our results in Section~\ref{sec:results}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Methodology of the Simulation}\label{sec:method}

@@

% how we simulated the spectrum
Below is our recipe for simulating \keck\ spectra and DSSTs:
\begin{enumerate}
\item Generate a synthetic spectrum for the target star using
  Spectroscopy Made Easy (SME;
  \citealt{valentipiskunov1996,valentifischer2005}; the SME spectra are
  kindly provided by Jason Curtis). We refer to this spectrum as the
  input synthetic spectrum or the SME spectrum.
\item Based on the SME spectrum, generate a deconcolved stellar
  spectral template (DSST) for the target
  star. First, we redshift the SME spectrum so that it has the same
  barycentric velocity as the real DSST of the target star. Then we
  break the SME spectrum into chunks as defined by the real DSST (an IDL
  structure) of this target star.
\item Run TERRASPEC \rev{\citep{Bender2012}, a versatile software for
  synthesizing telluric spectrum (it is a wrapper around the HITRAN line
  list \citep{hitran2013} and the LBLRTM package \citep{lblrtm},
  developed by Chad Bender, who provided crucial help in this work for
  using TERRASPEC)}, to generate a telluric absorption spectrum using a
  typical Mauna Kea atmospheric condition in the summer, with
  precipitable water vapor (pwv) 1~mm\footnote{As reported at
    \href{http://www.cfht.hawaii.edu/Instruments/ObservatoryManual/CFHT_ObservatoryManual_(Sec_2).html}{CFHT
  website}.}, and oxygen column density that is consistent
  with the altitude of the real DSST observation. We multiply this
  synthetic telluric spectrum with the SME spectrum to make a
  telluric-contaminated DSST.
\item Loop through each real observed spectrum of the target star, and
  simulate a pair of observations following this recipe:
  \begin{enumerate}
  \item Shift the SME spectrum to have the same barycentric velocity
    as the star at the epoch of the real observation (i.e., assuming
    intrinsic stellar velocity is zero).
  \item Generate a continuous wavelength solution for each echelle
      order based on the best-fit wavelength solution for the real
      spectrum. 
  \item Re-sample the SME spectrum and the iodine atlas onto a
    wavelength grid that is four times finer than the wavelength
    solution grid. Multiply the stellar spectrum with the iodine
    atlas.
  \item To add telluric contamination: multiply the simulated spectrum
    with a telluric absorption spectrum generated with TERRASPEC, again
    for typical Mauna Kea summer, with pwv $=$ 1~mm, and oxygen column
    density that is consistent with the altitude of the real observation.
  \item Determine the IP for each echelle order with two options: (1)
    a single Gaussian with $\sigma=1.7$ pixel, matching the \keck\
    resolution; (2) a sum-of-Gaussian IP derived using the average IPs for
    each echelle order. We will explain these two options later in the
    text.
  \item Convolve each order of the stellar$\times$iodine spectrum with
    the IP.
  \item Fit for the blaze function for each order of the real observed
    spectrum with a third-order polynomial using the top 1\% of the flux,
    and multiply the simulated spectrum so that they have matching ``blaze
    functions''. This also ensures that the simulated spectrum has the
    same photon counts as the real one.
  \item Add photon noise according to Poisson statistics, when
    desired.
  \end{enumerate}
\item Generate a separate data log file for each set of simulated of
  observations under the same conditions (i.e., telluric choice, IP choice,
  photon-noise choice).
\end{enumerate}

% different sets of simulations To isolate the problem of tellurics,
we first simulated spectra free of photon noise and with a simple
single Gaussian IP for the spectrograph ($\sigma = 1.7$ pixels to
match the \keck\ resolution). When extracting RVs for such sets of
simulated spectra, we fixed the IPs to the same as input and only
fitted for three free parameters. This removes the errors induced by
photon noise and uncertainties in IP fitting (which, after all,
involves 12 additional free parameters). We then added the Poisson
noise to the spectra, but still using simple and fixed IPs, to see how
the effects will change in cases with limited-SNR (as opposed to
infinite SNR). Next, we used complex IPs, the same ones as the
best-fit sum-of-Gaussian IPs found for real spectra, and float the IP
parameters when extracting RVs. \rev{For the simulated spectra with complex
IPs, we extracted their RVs following exactly the same procedure for
real observations, e.g., using IP initial guesses from solutions for
real neighboring B star $+$ iodine observations.} The conditions and
results of these three pairs of simulations are listed in
Table~\ref{tab:simulation}, and also illustrated in
Figure~\ref{fig:sim}. These results show the impacts of
telluric contamination on \keck\ data, which is discussed in the
following subsection.

%----------------------------------------------------------------
% Table: RV RMS for various simulations
\renewcommand{\arraystretch}{1.2} % more row spacing for the table
\begin{deluxetable*}{ccccl}
  \centering
\tabletypesize{\scriptsize}
\tablecaption{List of Simulations
\label{tab:simulation}}
\tablewidth{\textwidth}
\tablehead{
  \colhead{Simulation Conditions} & \colhead{Tellurics?} &
  \colhead{185144 RMS} &
  \colhead{10700 RMS} &
  \colhead{More Details in} 
}
\startdata
No photon noise, & No & 0.62 m/s & 1.95 m/s\tablenotemark{c} & Section~\ref{sec:results} \\ 
simple, fixed IPs & Yes & 1.21 m/s & 2.42 m/s\tablenotemark{c} & top
panels, Figure~\ref{fig:sim} \\ 
\hline
Poisson noise, & No & 2.11 m/s\tablenotemark{c} & 2.54 m/s\tablenotemark{c} & Section~\ref{sec:results} \\
simple, fixed IPs\tablenotemark{a} & Yes & 2.12 m/s\tablenotemark{c} & 2.81 m/s\tablenotemark{c} &
middle panels, Figure~\ref{fig:sim} \\ 
\hline
Poisson noise, & No & 1.22 m/s & 1.35 m/s & Section~\ref{sec:results}\\
complex, floating IPs,\tablenotemark{a} & Yes & 1.29 m/s & 1.44 m/s &
bottom panels, Figure~\ref{fig:sim} \\ 
\hline
Poisson noise, & No & 1.27 m/s & 1.43 m/s &Section~\ref{keck:telluric:masking} \\
complex, floating IPs, & Yes & 1.27 m/s & 1.43 m/s & Figure~\ref{fig:dsstmask} \\
masking the telluric pixels\tablenotemark{a} & & & & Table~\ref{tab:rmsmasking}  \\
\hline 
Poisson noise, & pwv $=$ 0.5, 0.9 & 1.28, 1.22 m/s & 1.32, 1.30 m/s &
Section~\ref{sec:model} \\ 
complex, floating IPs, & pwv $=$ 1.0, 1.1 & 1.25, 1.23 m/s & 1.33, 1.31
m/s & Figure~\ref{fig:neid} \\ 
modeling tellurics\tablenotemark{b} 
\enddata
\tablenotetext{a}{With pairs of simulated spectra with or without
  tellurics and each pair has the same Poisson noise added.}
\tablenotetext{b}{Telluric lines added with pwv $=$ 1~mm, and we
  extracted RVs using pwv $=$ 0.5, 0.9, 1.0, 1.1~mm to access how
  accurately/precisely one needs to model the tellurics.}
\tablenotetext{c}{These simulations suffer from severe numerical and
  algorithmic errors for reasons not yet fully understood.}
\end{deluxetable*}
%----------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results of the Simulation}\label{sec:results}

%----------------------------------------------------------------
% Telluric effect, no photon noise
% plot made by ~/Exo.../Keck.../simulate.../msplot.pro
\begin{figure*}
  \centering
\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-rja01-rjb01.eps}}
\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-rja01-rjb01.eps}}\
\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-rjc01-rjd01.eps}}
\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-rjc01-rjd01.eps}}\
\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-test0-test1.eps}}
\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-test0-test1.eps}}\
\caption{Effects of telluric lines manifested as correlation between
  RV and BC. Each point represents the difference in RV estimates for
  a pair of simulated spectra: one without telluric absorption, and
  one with telluric absorption on top of the stellar and iodine
  spectra. {\bf Top 2 panels:} To isolate the effects of telluric
  lines, the simulated spectra used for this plot do not have Poisson
  noise added, and they have simple one-component Gaussian IPs which
  have fixed width and thus the IP parameters are all fixed to the
  true values in the RV extraction. {\bf Middle 2 panels:} same as the
  top panels, but for simulated spectra with Poisson noise (same noise
  for the telluric and non-telluric spectrum pairs; and still the same
  simple IPs). {\bf Bottom 2 panels:} same as above, but for simulated
  spectra with Poisson noise and complex IPs that are similar to the
  ones in actual observations. IP parameters are not fixed in this
  case, so the code is fitting 12 additional parameters for the IP on
  top of the 3 for wavelength solution and Doppler shift.
\label{fig:sim}}
\end{figure*}
%----------------------------------------------------------------

% no photon noise
Figure~\ref{fig:sim} illustrates the effects of telluric
contamination under different conditions. The top panels are RV
differences between the simulated spectrum pairs with infinite SNR and
perfectly known IPs, which might somewhat represent the capability of
future precise RV instruments. These two plots highlight the net
effects of telluric contamination: they cause large biases in RV
estimates, which manifest as strong RV-BC correlations or
trends. \rev{Clearly, the current statistical weighting or ``vanking''
procedure in the Doppler code is unable to fully correct these biases.}

% adds photon noise?
Interestingly, when we added in photon noise (middle panels of
Figure~\ref{fig:sim}), the effects of telluric contamination
are washed out significantly. \rev{This is probably because photon noise
induces a much bigger RV scatter than the micro-telluric lines. This
is not surprising, given that the depths of these micro-telluric lines
are often comparable to noise level. We are still investigating the
exact reason of this ``wash out''.}

% adds complex IP 
When using complex IPs and fitting for IPs in RV extraction (bottom
panels of Figure~\ref{fig:sim}), the effects of telluric
contamination are further washed out, as we are adding in more errors
\rev{that are perhaps larger than telluric-induced ones}. We can
barely see any RV-BC correlation in the case of HD 185144 and only
some in HD 10700.

% tellurics add RV RMS
The RV-BC correlations shown in Figure~\ref{fig:sim} will
translate into spurious peaks in the periodograms of the target star,
and such spurious peaks will have periods around a sidereal year and
its harmonics. This is very damaging for the search of exoplanets in
the Habitable Zone around Sun-like stars, which would have periods
around 360 days. Besides these spurious signals, telluric
contamination also causes increases in RV RMS. In all cases of
telluric-free and telluric-contaminated simulation pairs, the RV RMS
is larger for the telluric-contaminated case
(Table~\ref{tab:simulation}). The RMS numbers written in
Figure~\ref{fig:sim} represent the amount of RV RMS added (in
quadrature) because of telluric contamination (again, the spectrum
pairs are same-noise pairs -- they only differ in terms of having or
not having telluric lines). These numbers also represent an RV RMS
floor set by the telluric contamination: for example, if we ignore
tellurics in RV reduction, one would not achieve an RV precision of
$<$0.6-0.7 m/s on G type stars using iodine cells as calibrators. This
would compromise our ability to detect Earth or super-Earth exoplanets
greatly (again, Earth 2.0 would have an RV amplitude of 0.08 m/s). In
the next section, we discuss strategies to eliminate these adverse
effects of telluric contamination for iodine-calibrated precise RV
data.

@@

%----------------------------------------------------------------
% Table: RV RMS for various simulations
\renewcommand{\arraystretch}{1.2} % more row spacing for the table
\begin{deluxetable}{ccl}
\tabletypesize{\scriptsize}
\tablecaption{Comparison of RV RMS between Simulations with or without Masking
\label{tab:rmsmasking}}
\tablewidth{280pt}
\tablehead{
  \colhead{HD 185144} & \colhead{HD 10700} & \colhead{Simulation Conditions}
}
\startdata
1.22 m/s & 1.35 m/s & No tellurics \\
1.29 m/s & 1.44 m/s & With tellurics \\
1.27 m/s & 1.43 m/s & No tellurics; with masking \\
1.27 m/s & 1.43 m/s & With tellurics; with masking
\enddata
\end{deluxetable}
%----------------------------------------------------------------

% what do I mean when I talk about masking?
The simplest solution is to mask out telluric lines in the spectrum,
which means, in practice, locate the telluric-contaminated pixels and
flag them as bad pixels in the observed spectrum so that the
least-$\chi^2$ fitter will ignore them. For \keck\ or any
iodine-calibrated RV reduction, this also means masking out the
regions corresponding to locations of telluric lines in the
deconvolved stellar reference spectrum -- because the stellar
reference spectrum was taken at a different BC, the telluric lines
therein are shifted with respect to the ones in the epoch observation
as we try to match up the stellar lines in observed and reference
spectra. This double masking procedure is illustrated in
Figure~\ref{fig:dsstmask}. This is done dynamically in
the fitting process, in the sense that, for each iteration in the
least-$\chi^2$ minimization process, the contaminated pixels are
located according to the current wavelength solution parameters in
this fitting iteration. The wavelength solution changes from iteration
to iteration, and thus the masked pixels can change too.

%----------------------------------------------------------------
% Double masking of telluric lines
% plot made by converting pdf to eps. pdf comes from slides of CfASSP
% seminar talk, which can be found in ~/Ex.../Professional../..CfASSP../.
\begin{figure}
\subfloat{\includegraphics[scale=0.3]{telluric/dsst-mask1.eps}}\\
\subfloat{\includegraphics[scale=0.3]{telluric/dsst-mask2.eps}}
\caption{Illustration for how we mask telluric contaminated
pixels. The top panel shows how we mask the telluric lines (red solid
lines) in the epoch observation taken at $t=t_e$. The bottom panel
shows why we also need to mask pixels associated with telluric lines
in the deconvolved stellar reference spectrum taken at epoch $t=t_0$
and being shifted in order to model the observation.
\label{fig:dsstmask}}
\end{figure}
%----------------------------------------------------------------

% simulations and results 
To investigate the effectiveness of masking, we performed RV
extraction on simulated spectra with or without telluric lines
injected and with or without masking (all with Poisson noise and
complex IP to mimic real observations as much as possible). For
stellar reference spectrum, we used the synthetic spectrum with
telluric lines. The results are already listed in
Table~\ref{tab:simulation}, but are listed again in
Table~\ref{tab:rmsmasking} for clear comparisons. In terms of
improving RV precision or reducing RV RMS, masking is very
ineffective. The additional errors it introduces diminish its
merits. On the other hand, masking does improve the accuracy to some
degree: for example, masking does remove the downward RV trend seen in
HD 10700 data on the bottom right plot of
Figure~\ref{fig:sim} in the BC range $[-3\times10^4,\
-2\times10^4]$ m/s. However, masking is an ineffective way to mitigate
the effects of telluric contamination overall, especially since the RV
errors and RV-BC trends are dominated by photon noise and algorithmic
errors (and other types of errors too in real observations).

@@

% how about masking in real observations?  
We also applied telluric masking in RV reduction for real
observations, and saw no improvement over RV precision or
accuracy. This is because other effects dominate rather than
tellurics, as mentioned above, such as photon and algorithmic errors
and especially deconvolution errors in stellar reference spectrum.

@@

%----------------------------------------------------------------
\subsection{How precisely does one need to model the tellurics?}\label{sec:model}
